Artin Group Presentations Arising from Cluster Algebras

### 2014-07-20 Paper.tex
Section 5 Edits

such that either
\begin{enumerate}
	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
	\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
we include the relation
\begin{align*}
	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}.
\end{align*}
Where subscripts are taken $\pmod d.$ 
\end{itemize}
\end{defn}

@@

\section{Symmetry among (R3') Relations}
\label{sec:one_relation}

As in \cite{BM13}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,

@@

\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
\end{lem}

\begin{proof}
As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
\begin{align*}
& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}
Furthermore, we obtain similar results for cycles containing edges of weight 2.
\begin{lem} 
Let $\Gamma$ be a diagram of finite type containing a 3-cycle as in (R3')(b) of ~\ref{grp def}. Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations (1) and (2) of (R3')(b) are equivalent, and they together imply the relation (3).
\end{lem}

\begin{proof}
The equivalence of (1) and (2) follows from the fact that
\begin{align*}
& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i}
\end{align*}

In showing that (1) and (2) imply (3), we will underline the terms being manipulated in each line for emphasis.
\begin{align*}
& s_{k}s_{j}s_{k}(s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k})s_{k}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{k}\underline{s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}\underline{s_{k}s_{k}^{-1}}s_{j}^{-1}s_{k}^{-1} \\
&= \underline{s_{k}s_{k}^{-1}}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}\underline{s_{j}^{-1}s_{k}s_{j}s_{k}}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}s_{k}s_{j}\underline{s_{k}s_{j}^{-1}s_{j}s_{k}^{-1}}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}\underline{e}s_{k}s_{j}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}s_{j}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= \underline{s_{i}s_{j}s_{i}}s_{j}^{-1}s_{k}s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{j}s_{i}\underline{s_{j}s_{j}^{-1}}s_{k}\underline{s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{j}s_{i}\underline{s_{k}s_{k}^{-1}}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}}s_{j}^{-1}s_{k}^{-1} \\
&= s_{j}\underline{s_{i}s_{i}^{-1}}s_{j}^{-1}s_{k}\underline{s_{j}s_{j}^{-1}}s_{k}^{-1} \\
&= \underline{s_{j}s_{j}^{-1}}\underline{s_{k}s_{k}^{-1}} \\
&= e
\end{align*}
\end{proof}

\begin{lem} 
Let $\Gamma$ be a diagram of finite type containing a 4-cycle as in (R3')(c) of ~\ref{grp def}. Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations (1) and (2) of (R3')(c) are equivalent.
\end{lem}

@@

@@

\begin{lem}\label{lem:op_homomorphism}
Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the inverse elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in W$_{\Gamma}$. To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$. But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$

For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r'(k, j) in W$_{\Gamma^{op}}$.

Finally, given a square labeled as in (R3')(c) and the relations r'(1, 2) and r'(3, 4), we have 
\begin{align*}
& s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{i}^{-1} \\
&= s_{i}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j})s_{j}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{j}^{-1}(s_{k}^{-1}s_{l}s_{k})s_{j}(s_{i}s_{j}^{-1}s_{i}^{-1}) \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{j}s_{j}^{-1}s_{i}^{-1}s_{j} \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}
\end{align*}
But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r'(j, i) in W$_{\Gamma^{op}}$. Therefore, we are done.
\end{proof}

>>>>

such that either
\begin{enumerate}
	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
	\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
we include the relation
\begin{align*}
	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
\end{align*}
where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
\end{itemize}
\end{defn}

@@

\section{Symmetry among (R3) Relations}
\label{sec:one_relation}

Given the relations (R2), many of the relations in (R3) become redundant. For example,

@@

\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}

so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2) and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3) hold for C.
\end{lem}

\begin{proof}
As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $A_{\Gamma}$ satisfies the relation r(0, 1). Then we have 
\begin{align*}
& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}
Furthermore, we obtain similar results for cycles containing edges of weight 2.
\begin{lem} \label{2tri}
Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:

\begin{tikzpicture}[baseline=-0.5ex]
   \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
  {
    && |[name = u]| {k} \circ& \\
    %
    &|[name=dl]|{j} \circ & &|[name=dr]| \circ {i} \\
  };
\draw[->]
  (u) to node[right] {2} (dr)
  ;
  \draw[->]
  (dl) to node[left]{2}(u)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;

   \end{tikzpicture}
and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, i) are equivalent.
\end{lem}

\begin{proof}
The lemma follows from the fact that
\begin{align*}
& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i}
\end{align*}
\end{proof}

In the setting of the previous lemma, we also obtain the following relation, which will play an important role in later proofs.

\begin{lem}
Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that 
$$s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
\end{lem}

\begin{proof}
We first show that 
$$s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$ 
The result then follows by inverting the relation and conjugating by $s_{j}$. In the following computation, we will underline the terms being manipulated in each line for emphasis.

\begin{align*}
& s_{k}s_{j}s_{k}(s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k})s_{k}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{k}\underline{s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}\underline{s_{k}s_{k}^{-1}}s_{j}^{-1}s_{k}^{-1} \\
&= \underline{s_{k}s_{k}^{-1}}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}\underline{s_{j}^{-1}s_{k}s_{j}s_{k}}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}s_{k}s_{j}\underline{s_{k}s_{j}^{-1}s_{j}s_{k}^{-1}}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}\underline{e}s_{k}s_{j}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{i}s_{j}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= \underline{s_{i}s_{j}s_{i}}s_{j}^{-1}s_{k}s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{j}s_{i}\underline{s_{j}s_{j}^{-1}}s_{k}\underline{s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
&= s_{j}s_{i}\underline{s_{k}s_{k}^{-1}}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}}s_{j}^{-1}s_{k}^{-1} \\
&= s_{j}\underline{s_{i}s_{i}^{-1}}s_{j}^{-1}s_{k}\underline{s_{j}s_{j}^{-1}}s_{k}^{-1} \\
&= \underline{s_{j}s_{j}^{-1}}\underline{s_{k}s_{k}^{-1}} \\
&= e
\end{align*}
\end{proof}

\begin{lem} \label{2sqr}
Let $\Gamma$ be a diagram of finite type containing the following 4-cycle: 
\begin{tikzpicture}[baseline=-0.5ex]
\matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|{i}\circ& |[name = ur]|\circ{j}\\
    %
    &|[name=dl]|{l} \circ &|[name=dr]| \circ{k} \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ; 
\end{tikzpicture}
and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, l) are equivalent.
\end{lem}

@@

As a result of these lemmas, we immediately obtain the following corollary:

\begin{cor}
Let $\Gamma$ be a diagram of finite type. Then the group A($\Gamma$) defined in the introduction is isomorphic to the group A$_{\Gamma}$
\end{cor}

@@

\begin{lem}\label{lem:op_homomorphism}
Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
\end{lem}
\begin{proof}
One can see that the inverse elements satisfy (R2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$. To see that the elements satisfy (R3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3) in A$_{\Gamma}$. But then applying relations from (R2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in A$_{\Gamma^{op}}.$

For a triangle labeled as in ~\ref{2tri}, by the relation r(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r(k, j) in A$_{\Gamma^{op}}$.

Finally, given a square labeled as in ~\ref{2sqr} and the relations r(1, 2) and r(3, 4), we have 
\begin{align*}
& s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{i}^{-1} \\
&= s_{i}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j})s_{j}^{-1}s_{i}^{-1} \\
&= s_{i}s_{j}s_{j}^{-1}(s_{k}^{-1}s_{l}s_{k})s_{j}(s_{i}s_{j}^{-1}s_{i}^{-1}) \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{j}s_{j}^{-1}s_{i}^{-1}s_{j} \\
&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}
\end{align*}
But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
\end{proof}
